---
title: "Data_Science"
author: "Andrew Harvey"
date: "18 May 2024"
format: html
editor: visual
---

## Part 1
1. What do you think being a data scientist is about?

**I think that being a data scientist means that you are a professional who specializes in taking unstructured data, organizing it, preforming some analysis or fitting to help enable a decision, find a trend, or predict an outcome. **

2. What differences/similarities do you see between data scientists and statisticians?

**One of the largest differences between statisticians is the scope of work. A statistician's primary responsibility is to preform statistical analysis on quantitative, numeric, data that is organized in some fashion. A data scientist on the other hand also deals in qualitative, non-numeric, data. Statisticians and data scientists share many task such as data wrangling, performing analysis, and making recommendations but the incorporation of digital non-numeric data such as images and categorical information is unique to data scientist. **

3. How do you view yourself in relation to these two areas?

**I see myself as more of a data scientist rather than a statistician. While much of my field is based in modeling, analyzing numeric data, and probability. The incorporation of non-numerical data and other non-mathematical tasks in data science align with me more.  **

## Part 2

|   The following code chunk will use the density function on the variable "Sepal.Length" in the data set "iris" and store it in the object "y".
```{r store y}
#given line of code
y <- density(iris$Sepal.Length)
```

|    The following code chunk will display the class, type, and structure of the object "y".

```{r information on y}
#create an R code chunk to determine the class, type, and structure of the object y
class(y)
typeof(y)
str(y)
```
|   The graph below is made using the plot function on the object "y". The code chunk is hidden by setting echo to false. 
```{r plot y}
#| echo: false
plot(y)
```